Multi-product Batch Processing Time Maximization Problem

### 2023-07-27 cover.tex
updating files

\begin{letter}{To Applied Mathematical Modelling journal}
    \setkomavar{subject}{Cover letter}
    \opening{Dear editor,}

@@

The problem was identified by me during the development of a solver for production planning in extruders.

As I am applying a local search heuristic, at each iteration I need to generate a new solution, and therefore I need to solve the MPBPTM problem.

I had a vague idea about the proposed analytical method while I was presenting the problem to my co-workers, and I managed to develop the method the same day before going to sleep, as I was really excited about the idea of the method and about the impact that this method would generate for the performance of the solver I'm developing.

According to the bibliographic research carried out by the authors of the mentioned paper, the problem has not yet been presented in the scientific literature.

However, the mathematical model and, in particular, the analytical method developed for the MPBPTM problem are also very important scientific contributions.

The language used in the paper is simple, so that many researchers can easily understand the work.

I am then waiting for your final decision with great expectation of approval of the work for publication in the Applied Mathematical Modelling journal.	
    \closing{Sincerely,}
  \end{letter}
\end{document}

>>>>

\begin{letter}{To Simulation Modelling Practice and Theory}
    \setkomavar{subject}{Cover letter}
    \opening{Dear editor,}

@@

MPBPTM is a combinatorial optimization problem. The complexity of MPBPTM is mainly attributed to the fact that there is a production limit for the set of products and not just for each product. This restriction causes the problem to be defined as a non-polynomial problem.

The problem was identified by me during the development of a solver for production planning in extruders. As I am applying a local search heuristic, at each iteration I need to generate a new solution, and therefore I need to solve the MPBPTM problem.

However, MPBPTM is also a practical problem and its solution directly influences the efficiency of inventory control in some industries, as is the case of industries in the plastic bag sector.

As is widely known, there are few combinatorial optimization problems that can be solved using exact methods. In this paper we present an exact optimization method for solving the MPBPTM problem, based on the idea of partitioning the problem into two smaller problems.

I had a vague idea about the proposed method while I was presenting the problem to my co-workers, and I managed to develop the method the same day before going to sleep, as I was really excited about the idea of the method and about the impact that this method would generate for the performance of the solver I'm developing for production planning in extruders.

According to the bibliographic research carried out by the authors, the problem and exact method proposed in this paper has not yet been presented in the scientific literature.

Also, the language used in the paper is simple, so that many researchers can easily understand the work.

I am then waiting for your final decision with great expectation of approval of the work for publication in this journal.	
    \closing{Sincerely,}
  \end{letter}
\end{document}

### 2023-07-27 manuscript.tex
updating files

\begin{frontmatter}

%% Title, authors and addresses

@@

\affiliation[label1]{organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
             city={Caruaru},
             postcode={55014-900},
             state={PE},
             country={Brasil}}

%\affiliation{organization={},%Department and Organization
%            addressline={}, 
 %           city={},
 %           postcode={}, 
 %           state={},
 %          country={}}

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem. We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}

%%Graphical abstract
\begin{graphicalabstract}
\includegraphics[width=13cm]{graphical.png}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item brief bibliographic review on multi-product batch problems;
\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
\item linear integer programming model for the MPBPTM problem;
\item polynomial time complexity analytical method for solving the MPBPTM problem.
\end{highlights}

\begin{keyword}
multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
%% keywords here, in the form: keyword \sep keyword

%% PACS codes here, in the form: \PACS code \sep code

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}

@@

The scientific literature presents several papers that address multi-product batch problems. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. \cite{MendezEtAll2000} and \cite{ShiEtAll2017} present two parallel multi-product batch scheduling (PMPBS) problems, in which production units of the same type are arranged in parallel, forming each production stage. In this case, it is also necessary to define in which units each product will be processed. The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance). In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

In this work, we are concerned with determining the ideal processing time for a batch consisting of a set of products, each product being or not different from the other products of the same batch. That is, we consider a specific case where different products are processed simultaneously on the same processor. This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.

@@

\section{Fraga's analytical solution}
\label{sec:analyticalSol}

@@

To test the developed model and analytical solution method, we created a solver in C++ (https://github.com/blinded) and a solver in LINGO (https://github.com/blinded). The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\

@@

\section{Contributions to this work}
\label{sec:contributions}

The work for the elaboration of this paper was carried out by tree contributors, as described below. Blinded, developed the detailed study on the plastic bag production process, which made it possible to identify the problem addressed in this paper. Blinded was responsible for identifying the problem, mathematical modeling, proposing an analytical solution, developing a solver in C ++ for applying the analytical solution and a solver in LINGO for validating the mathematical model and the results found by the first solver, developing benchmarks, and testing the model and analytical method proposed, as well as surveying bibliography and elaboration of the paper. Blinded contributed to the bibliographic survey. The authorship of this work is distributed according to contributions described.

@@

@@

Blinded.
%We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects. We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process. Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects. We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.

@@

>>>>

\begin{frontmatter}
%% Title, authors and addresses

@@

%\affiliation[label1]{
%			 organization={Centro Acadêmico do Agreste - Universidade Federal de Pernambuco},
%             addressline={Avenida Marielle Franco, Bairro Nova Caruaru},
%             city={Caruaru},
%             postcode={55014-900},
%             state={PE},
%             country={Brasil} }

\affiliation[label1]{
		   organization={Agreste Academic Center - Federal University of Pernambuco},%Department and Organization
           addressline={Avenida Marielle Franco, Nova Caruaru}, 
           city={Caruaru},
           postcode={55014-900}, 
           state={PE},
           country={Brazil}}

\begin{abstract}
In the plastic bag extrusion process, it is necessary to determine the optimal processing time for batches formed by different products, which are processed simultaneously by the same extruder, but with different processing rates. The batch processing time must be determined in order to meet a series of known constraints, such as the limitation for the quantity produced for each product and for the quantity produced for the set of all products in the same batch. In this paper we present this problem as a new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem. We also present a mathematical model for the MPBPTM problem and an analytical solution method with polynomial time complexity, which proved to be able to obtain optimal solutions for several benchmarks in a very short time, even for very large instances.
\end{abstract}
%%Graphical abstract
\begin{graphicalabstract}
\includegraphics[width=0.8\textwidth]{graphical.png}
\end{graphicalabstract}

%%Research highlights
\begin{highlights}
\item brief bibliographic review on multi-product batch problems;
\item new combinatorial optimization problem named Multi-product Batch Processing Time Maximization (MPBPTM) problem;
\item linear integer programming model for the MPBPTM problem;
\item exact optimization method for solving the MPBPTM problem.
\end{highlights}

\begin{keyword}
multiproduct batch \sep processing time maximization \sep analytical solution \sep C++ \sep LINGO
\end{keyword}
\end{frontmatter}

@@

The scientific literature presents several papers that address multi-product batch problems. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine the production sequence of the products and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. \cite{MendezEtAll2000} and \cite{ShiEtAll2017} present two parallel multi-product batch scheduling (PMPBS) problems, in which production units of the same type are arranged in parallel, forming each production stage. In this case, it is also necessary to define in which units each product will be processed. The authors also take into account other constraints for the problem (\emph{e.g.}, release time and due date for the products, and sequencing constraints due to mismatched product colors sequences) and other goals (\emph{i.e.}, optimize customer satisfaction and/or the plant performance). In the papers mentioned above, production in a single unit or in a serial flowshop plant is considered, in which all products follow a linear flow through the production stages. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in lines, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time. \cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints. In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine. However, there are no production limitations for the production of each product group. The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).

In this work, we are concerned with determining the ideal processing time for a single batch consisting of a set of products, each product being or not different from the other products of the same batch. That is, we consider a specific case where different products are processed simultaneously on the same processor. This case occurs, for example, during the processing of plastic bags in extruders, where the resins are melted, then pass through a cylinder forming a balloon and this balloon, after cooling, is stored in a coil which, in turn, is cut into several smaller coils with different models of plastic bags.

@@

\section{Analytical solution}
\label{sec:analyticalSol}

@@

To test the developed model and analytical solution method, we created a solver in C++ and a solver in LINGO (https://github.com/tbfraga/COPSolver). The tests were performed on a notebook with an Intel i7 processor. We tested the solvers developed for the benchmarks presented on Tables \ref{tab:MBPTMP001}, \ref{tab:MBPTMP002} and \ref{tab:MBPTMP003}, and for randon benchmarks generated by the following functions: \\

@@

@@

\section{CRediT authorship contribution statement} 
\label{sec:contributions}

T.B. Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing. Í.R.B. Aquino: Data curation. R.C.S. Menêzes: Data curation.

@@

We are enormously grateful to Coordenação de Aperfeiçoamento de Pessoal de Nível Superior (CAPES) and to Conselho Nacional de Desenvolvimento Científico e Tecnológico (CNPq) for the financial support provided to our projects. We also thank LINDO systems team for the LINGO software license, without which this work would not have been possible and the to the owner of the company in the plastics sector, who allowed us to learn about his company's production process. Finally, we would like to thank Pró-reitoria de Extensão e Cultura da UFPE (PROExC) and the Research Director of Propesqi (Pró-reitoria de Pesquisa e Inovação da UFPE) for their support and recognition of our work, and dear Professors Antônio José da Silva Neto and João Flávio Vieira de Vasconcellos from IPRJ/UERJ, who contributed significantly to the formation of essential skills for the development of our projects. We also thank my co-worker Marcos Luiz Henrique, for having helped by evaluating the mathematical model and solution method proposed in this paper.

@@

\bibitem[\protect\citeauthoryear{Li et al.}{2022}]{LiEtAl2022}
Li, C., Wang, F., Gupta, J.N.D., Chung, T. (2022). Scheduling identical parallel batch processing machines involving incompatible families with different job sizes and capacity constraints. {\it Computers \& Industrial Engineering}, Vol. 169, pp. 108115.
